### 2018-07-19 paper/global-overlay-design.tex
WIP on design
WIP edits in global-overlay-design.tex

\subsection{\Acfp*{SPOR}}%
\label{sec:global_overlay}
\label{sec:message_passing}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
  \caption{\label{fig:file-exchange}%
    A schematic of Alice and Bob sending a message using \name.
    \ding{1} illustrates the layer of the headers that Alice and Bob create.
    In \ding{2}, Alice and Bob exchange the headers out-of-band.
    In \ding{3}, Alice and Bob use two \ac{SPOR} routes, one for messages and 
    one for acknowledgements.
  }
\end{figure}

@@

@@

To reach this goal, we employ Random Peer Sampling (RPS) \cite{Voulgaris_Gavidia_van_Steen_2005,Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}.
Essentially, each node maintains a view \view containing \viewsize other devices' descriptors. 
This view is periodically updated as follows: a device $d$ pops the oldest descriptor $d'$ from its view, then swaps a predefined number of $l$ elements from \view with $d'$.
Both devices add a descriptor for themselves to the view exchange.
If $d'$ was offline, its descriptor is simply removed from the $d$'s view, but \view is otherwise not updated.

@@

In \name, an RPS descriptor for device $d$ is constituted of the following information:
\begin{itemize}
  \item Its address: $d$;
  \item Its public key: \(\pk_d\);
  \item Its probability of being online in the near future, as provided by the Squad Overlay: $p_d=P\left[d \in O_{t+1} | S_t\right]$.
\end{itemize}

Devices now have all the information they need to establish reliable PORs.

@@

% \NewAlgorithm{\GetRandomPeer}{GetRandomPeer}

>>>>

\subsection{\Acf*{SPOR}}%
\label{SPOR}%
\label{sec:global_overlay}%
\label{sec:message_passing}%

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
  \caption{\label{fig:file-exchange}%
    A schematic of Alice and Bob sending a message using \name.
    \ding{182} illustrates the layer of the headers that Alice and Bob create.
    In \ding{183}, Alice and Bob exchange the headers out-of-band.
    In \ding{184}, Alice and Bob use two \ac{SPOR} routes, one for messages and 
    one for acknowledgements.
  }
\end{figure}

@@

\NewAlgorithm{\GetRandomPeer}{GetRandomPeer}

We assume that there is an algorithm \(\GetRandomPeer\) which returns one 
uniformly randomly selected node.
Each such node includes
\begin{itemize}
  \item the node's identifier (address), \(d\);
  \item the node's public key, \(\pk_d\);
  \item the node's probability of being online in the near future, \(p_d = 
      \Pr\left(d \in O_{t+1} | S_t\right)\).
\end{itemize}

@@

To reach this goal, we employ Random Peer Sampling (RPS)~\cite{Voulgaris_Gavidia_van_Steen_2005,Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}.
Essentially, each node maintains a view \view containing \viewsize other devices' descriptors. 
This view is periodically updated as follows: a device $d$ pops the oldest descriptor $d'$ from its view, then swaps a predefined number of $l$ elements from \view with $d'$.
Both devices add a descriptor for themselves to the view exchange.
If $d'$ was offline, its descriptor is simply removed from the $d$'s view, but \view is otherwise not updated.

@@

@@
